Providing better confidentiality and authentication on the Internet using Namecoin and MinimaLT

### 2014-01-10 paper.tex
Use gender-neutral pronouns.

When someone succeeds in solving this problem, he sends his solution to the network. Nodes verify if that answer is valid, and if it is, they broadcast it to their peers. It progressively spreads across all nodes and is added to the network's blockchain.

@@

A few months ago, a previously unknown email provider called \emph{Lavabit} was under pressure from the US government to hand over its private SSL key. The reason turned out to be that Edward Snowden was using the email service. If Lavabit had turned over the SSL keys, they would have compromised the privacy of their entire user base. This is due to poorly configured SSL where the ECDHE is not the default. ECDHE performs an Elliptic curve Diffie-Hellman key exchange. The last E from ECDHE stands for Ephemeral which means that a new key, that will never be stored, is generated at every handshake. Hence, even if the server gets compromised or the network operator is forced to hand over an encryption key, he won't be able to provide it. Unfortunately, most system administrators don't put the \emph{ECDHE} ciphers on top of their ciphers list resulting in the lack of Perfect Forward Secrecy.

@@

Let's say a client \emph{C} wants to connect to a server \emph{S}. \emph{C} uses the Namecoin blockchain to get its identity, and an ephemeral key of \emph{S}. Now \emph{C} sends his first packet to \emph{S} containing his newly-generated ephemeral key, a new tunnel ID and the first bits of data. This segment's body can be encrypted using the ephemeral key of the server we retrieved previously ephemeral keys will no more be used past this point because both clients can now compute a shared secret by performing a Diffie-Hellman Key exchange with the public ephemeral keys they exchanged. In the future, this shared secret will be used to perform symmetric encryption between both hosts.

@@

When a client initiates a rekey, he generates a new tunnel ID and sends it to the server as a call. Like the initial tunnel establishment procedure, the client generates a new key pair and sends his new public key along with the new tunnel ID to the server using the current encrypted tunnel. The corresponding private key of the pair that was generated will never be used (it actually doesn't even need to be known), its only function is to make the packet look like a regular tunnel initialisation packet. Now that the new tunnel is ready, the client can send packets to the new tunnel ID. But what encryption key should be used now? MinimaLT avoids doing a DH on rekeying for performance reasons, thus, client is hashing with a cryptographically secure hash function the old symmetric encryption key to generate the next one. The client will include the temporarily generated public key inside the encrypted packet sent to the server. Once the server gets a packet on the new tunnel ID, it will perform the same hashing as the client did to compute the decryption key. Now the server can decrypt the packet and it has to verify that the key is matching the previously sent one in the (\emph{$\text{nextTid}_{0}$}) call. This verification is required\cite{MinimaLT} because otherwise an active attacker could alter the key sent in the tunnel announce packet and then sent a second packet with the matching DH computer key and notice that it would fail. He could conclude that this would be a rekeying procedure and not the creation of a new tunnel.

>>>>

When someone succeeds in solving this problem, they sends their solution to the network. Nodes verify if that answer is valid, and if it is, they broadcast it to their peers. It progressively spreads across all nodes and is added to the network's blockchain.

@@

A few months ago, a previously unknown email provider called \emph{Lavabit} was under pressure from the US government to hand over its private SSL key. The reason turned out to be that Edward Snowden was using the email service. If Lavabit had turned over the SSL keys, they would have compromised the privacy of their entire user base. This is due to poorly configured SSL where the ECDHE is not the default. ECDHE performs an Elliptic curve Diffie-Hellman key exchange. The last E from ECDHE stands for Ephemeral which means that a new key, that will never be stored, is generated at every handshake. Hence, even if the server gets compromised or the network operator is forced to hand over an encryption key, they won't be able to provide it. Unfortunately, most system administrators don't put the \emph{ECDHE} ciphers on top of their ciphers list resulting in the lack of Perfect Forward Secrecy.

@@

Let's say a client \emph{C} wants to connect to a server \emph{S}. \emph{C} uses the Namecoin blockchain to get its identity, and an ephemeral key of \emph{S}. Now \emph{C} sends its first packet to \emph{S} containing its newly-generated ephemeral key, a new tunnel ID and the first bits of data. This segment's body can be encrypted using the ephemeral key of the server we retrieved previously ephemeral keys will no more be used past this point because both clients can now compute a shared secret by performing a Diffie-Hellman Key exchange with the public ephemeral keys they exchanged. In the future, this shared secret will be used to perform symmetric encryption between both hosts.

@@

When a client initiates a rekey, it generates a new tunnel ID and sends it to the server as a call. Like the initial tunnel establishment procedure, the client generates a new key pair and sends its new public key along with the new tunnel ID to the server using the current encrypted tunnel. The corresponding private key of the pair that was generated will never be used (it actually doesn't even need to be known), its only function is to make the packet look like a regular tunnel initialisation packet. Now that the new tunnel is ready, the client can send packets to the new tunnel ID. But what encryption key should be used now? MinimaLT avoids doing a DH on rekeying for performance reasons, thus, client is hashing with a cryptographically secure hash function the old symmetric encryption key to generate the next one. The client will include the temporarily generated public key inside the encrypted packet sent to the server. Once the server gets a packet on the new tunnel ID, it will perform the same hashing as the client did to compute the decryption key. Now the server can decrypt the packet and it has to verify that the key is matching the previously sent one in the (\emph{$\text{nextTid}_{0}$}) call. This verification is required\cite{MinimaLT} because otherwise an active attacker could alter the key sent in the tunnel announce packet and then sent a second packet with the matching DH computer key and notice that it would fail. It could conclude that this would be a rekeying procedure and not the creation of a new tunnel.
